Modeling Two Body Collisions with Spring Potential Interactions

### 2014-12-13 paper/paper.tex

\section{Results}
\subsection{Simulation Performance}
\subsubsection{Default Configuration}
One of the first tasks was to validate the simulation framework using a system where the physics was simple and easy to intuitively predict. This system uses a stationary target of radius 2, with a projectile of radius 1 incoming at velocity 5 with an impact parameter of 1. The objects have equal density. We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ force constant. To begin to get an understanding of the collision we first plot each objects center of mass trajectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}). The projectile rebounds off the target sending it off at a slow velocity in the oposite direction will the systems center of mass steadly moves in a straight line.
\begin{figure}[h!]
  \includegraphics[width=.45\textwidth]{plots/default/x_vs_y_with_ellipse.pdf}
  \includegraphics[width=.45\textwidth]{plots/default/x_vs_y_with_ellipse_MS.pdf}
                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
                  \caption{(L) The initial state of the system when the objects come in contact. The collections of points (which form a continuous line) show the position of the center of each object at each time step while the objects are in contact. (R) The state of the system when the objects are at a minimum separation i.e. maximum $\Delta x$ from equilibrium.}
                  \label{fig:tracks_default}
\end{figure}

>>>>

\section{Results}
\subsection{Simulation Performance}
\subsubsection{Default Configuration}
One of the first tasks was to validate the simulation framework using a system where the physics was simple and easy to intuitively predict. This system uses a stationary target of radius 2, with a projectile of radius 1 incoming at velocity 5 with an impact parameter of 1. The objects have equal density. We configure this system to have no energy loss ($\eta = 0$), $\lambda=1$ power law, and $k=100$ force constant. $\Delta t = 0.001$ was found to give sufficent precision for most studies and is the default $\Delta t$ value for all simulations unless otherwise noted. To begin to get an understanding of the collision we first plot each objects center of mass trajectory during the time when they are in contact with each other and are undergoing accelerations (Figure~\ref{fig:tracks_default}). The projectile rebounds off the target sending it off at a slow velocity in the oposite direction while the systems center of mass moves steadly in a straight line.
\begin{figure}[h!]
  \includegraphics[width=.45\textwidth]{plots/default/x_vs_y_with_ellipse.pdf}
  \includegraphics[width=.45\textwidth]{plots/default/x_vs_y_with_ellipse_MS.pdf}
                  {\par\nobreak\rule[9pt]{35em}{0.5pt}\vspace{-5mm}}
                  \caption{(L) The initial state of the system when the objects come in contact. The collections of points (which form a continuous line) show the position of the center of each object at each time step while the objects are in contact. (R) The state of the system when the objects are at a minimum separation i.e. maximum $\Delta x$ from equilibrium.}
                  \label{fig:tracks_default}
\end{figure}
